Energy Regulation for Biologically-Inspired Robotics

### 2021-09-20 latex/nserc/proposal.tex
Made proposal in letter paper size, not A4 size
Final update of proposal, thanks to Rushay

%----------- Choose Margins ----------%
\usepackage[a4paper,margin=1.87cm]{geometry}

@@

\vspace{-1.2cm} % Move the following text up
%\textbf{What is your area of research? What sort of problems do you want to
%    address? WHy is the area important, and why are the applications important?
%    What is special about your approach, and how is it different from
%    existing/competing approaches? What is a sample application of the outcomes
%of your thesis?}
%\textbf{Detailed but concise. Provide background to position your research
%    within current knowledge of the field. State significance of research to the
%    field. Outline approach to be taken (citing literature). Clearly state
%differences btwn masters and this work.}

@@

There are two types of constraints on a mechanical system:
\textit{holonomic} constraints restrict position (e.g. a snake robot can slither
on the ground but cannot fly),
while \textit{nonholonomic} constraints restrict both position and
velocity (e.g. an autonomous car with normal wheels cannot slide sideways).
It is often possible to use a robot's actuators to enforce a desired constraint
which is engineered to achieve a safety or motion planning goal.
Since this constraint is enforced by the robot's actuators, and not by the
physics of the system, it is known as a ``virtual" constraint
\cite{vhcs_for_el_systems}.
Virtual holonomic constraints (VHCs) have been used to control walking robots
\cite{stable_walking}, autonomous bicycles \cite{bicycle},
helicopters \cite{helicopter}, and snake robots \cite{snake_robot},
among other applications.
Unfortunately, VHCs cannot adequately recreate many animal behaviours.
For example, they cannot perfectly recreate the giant motion of gymnastics 
because they do not incorporate information about the gymnast's velocity
\cite{xingbo_thesis}.
This is where virtual nonholonomic constraints (VNHCs) are most useful.

@@

\newpage

@@

Using VNHCs for \textit{energy injection} is beneficial because it allows robots to
safely and reliably increase their momentum.
Likewise, designing VNHCs for \textit{energy dissipation} allows robots to
safely and realistically slow down.
In this PhD, I propose to further study the energy regulation properties of VNHCs.
First, we will find mathematical conditions under which VNHCs are guaranteed to
inject or dissipate energy in fixed-base robots.
Then we will design a means of transitioning between two different VNHCs,
enabling us to regulate a robot's energy in a provably safe manner.
We will experimentally verify the results of this theory on the acrobot by
designing a gymnastics routine which is performed solely by transitioning
between different virtual constraints.
Finally, we will extend the theory to mobile animal-like robots,
and we will build a robotic monkey which uses VNHCs to swing on monkey bars just
like a real monkey would swing through jungle trees.

>>>>

%----------- Choose Margins ----------%
\usepackage[margin=1.87cm]{geometry}

@@

\vspace{-1.5cm} % Move the following text up
%\textbf{What is your area of research? What sort of problems do you want to
%    address? WHy is the area important, and why are the applications important?
%    What is special about your approach, and how is it different from
%    existing/competing approaches? What is a sample application of the outcomes
%of your thesis?}
%\textbf{Detailed but concise. Provide background to position your research
%    within current knowledge of the field. State significance of research to the
%    field. Outline approach to be taken (citing literature). Clearly state
%differences btwn masters and this work.}

@@

There are two types of constraints on a mechanical system:
\textit{holonomic} constraints restrict position (e.g. an autonomous car must
remain on the ground),
while \textit{nonholonomic} constraints restrict position and
velocity (e.g.~an autonomous car with normal wheels cannot slide sideways).
It is often possible to use a robot's actuators to enforce a desired constraint
which is engineered to achieve a safety or motion planning goal.
Since this constraint is enforced by the robot's actuators, and not by the
physics of the system, it is known as a ``virtual" constraint
\cite{vhcs_for_el_systems}.
Virtual holonomic constraints (VHCs) have been used to control walking robots
\cite{stable_walking}, autonomous bicycles \cite{bicycle},
helicopters \cite{helicopter}, and snake robots \cite{snake_robot},
among other applications.
Unfortunately, VHCs cannot adequately recreate many animal behaviours.
For example, they cannot perfectly recreate the giant motion of gymnastics 
because they do not incorporate information about the gymnast's velocity
\cite{xingbo_thesis}.
This is where virtual nonholonomic constraints (VNHCs) become useful.

@@

@@

Using VNHCs for \textit{energy injection} is beneficial because it allows robots to
safely and reliably increase their momentum.
Likewise, designing VNHCs for \textit{energy dissipation} allows robots to
safely and realistically slow down.
In this PhD, I propose to further study the energy regulation properties of VNHCs.
First, we will find mathematical conditions under which VNHCs are guaranteed to
inject or dissipate energy in fixed-base robots.
Then we will design a means of transitioning between two different VNHCs,
enabling us to regulate a robot's energy in a provably safe manner.
We will experimentally verify the results of this theory on the acrobot by
designing a gymnastics routine which is performed solely by transitioning
between different virtual constraints.
Finally, we will extend the theory to mobile animal-like robots,
and we will build a robotic monkey which uses VNHCs to swing on monkey bars just
like a real monkey would swing through jungle trees.
This robot monkey is representative of a variety of robotic systems, and will be
a useful platform on which to test our mathematical theory.
